---
title: "aco"
author: "Batta Liu"
date: "September 20, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### take a look at the ACO data
```{r}
opts_chunk$set(results = "hide")
library(readr)
suppressMessages(library(dplyr))
library(knitr)
require("RPostgreSQL")
```

```{r}
aco.part <- read.csv(file = "aco/aco-participant.csv", header = TRUE, sep = ",") 
aco <- read.csv(file = "aco/aco-list.csv", header = TRUE, sep = ",") #397

part.cnt <- aco.part %>% 
	group_by(ACO.Legal.or.Name.Doing.Business.As, Public.Contact.Phone) %>% 
	tally()

```
check whether two lists have same number of ACOs
```{r}
anti_join(aco, part.cnt, by = "ACO.Legal.or.Name.Doing.Business.As") #2
anti_join(part.cnt, aco, by = "ACO.Legal.or.Name.Doing.Business.As")
test <- inner_join(part.cnt, aco, by = "ACO.Legal.or.Name.Doing.Business.As")
```
found that 2 ACOs don't have data of participants,check why ???????
* Accountable Care Partners, LLC
* Emerald Physicians

found that two ACOs are duplicate
* Baroma Health Partners
* Mercy ACO, LLC
```{r, results = "markup"}
str(unique(aco$ACO.Legal.or.Name.Doing.Business.As))
test <- table(aco$ACO.Legal.or.Name.Doing.Business.As)
which(test==2)
# which(aco$ACO.Legal.or.Name.Doing.Business.As=="Baroma Health Partners")
# which(aco$ACO.Legal.or.Name.Doing.Business.As=="Mercy ACO, LLC")
aco[aco$ACO.Legal.or.Name.Doing.Business.As=="Baroma Health Partners",] # same info but different ACO.Service.Area and public.contact.phone
aco[aco$ACO.Legal.or.Name.Doing.Business.As=="Mercy ACO, LLC",] # totally different info

```
find ACOs serving a targeted state,e.g.,CA
```{r}
CA.ACO <- as.character(aco$ACO.Legal.or.Name.Doing.Business.As[grep("CA", aco$ACO.Service.Area)])
CA.only.ACO <- as.character(aco$ACO.Legal.or.Name.Doing.Business.As[aco$ACO.Service.Area=="CA"])
part.cnt[part.cnt$ACO.Legal.or.Name.Doing.Business.As=="Baroma Health Partners",]
test <- data.frame(aco.part[aco.part$ACO.Legal.or.Name.Doing.Business.As=="Baroma Health Partners",])
# write_csv(test, path = "part_name.csv")
```

### find out the aco participant npi.
```{r NPPES}
pw <- {
	"no323232"
}

# loads the PostgreSQL driver
drv <- dbDriver("PostgreSQL")

# creates a connection to the postgres database
# note that "con" will be used later in each connection to the database
con <- dbConnect(drv, dbname = "liubatta",
								 host = "192.168.0.10", port = 5432,
								 user = "liubatta", password = pw)

rm(pw) # removes the password
# check for the cartable
dbExistsTable(con, "tmp_test")
df.nppes <- dbGetQuery(con, 
												" SELECT npi_id, entity_type_code,
												provider_organization_name_legal_business_name,
					 							provider_first_name, provider_middle_name,
												provider_last_name_legal_name
												from npi_20160710")
```

```{r, eval=FALSE}
df.nppes.clean <- df.nppes %>% 
	select(npi_id, entity_type_code,
												provider_organization_name_legal_business_name,
					 							provider_first_name, provider_middle_name,
												provider_last_name_legal_name)
```


```{r}


df.nppes$new.name <- gsub("&"," and ", df.nppes$provider_organization_name_legal_business_name)
df.nppes$new.name <- gsub("\\.", "", df.nppes$new.name)
df.nppes$new.name <- gsub("[[:punct:]]"," ", df.nppes$new.name)
df.nppes$new.name <- toupper(df.nppes$new.name)
df.nppes$new.name2 <- gsub("[[:space:]]+"," ", df.nppes$new.name)
df.nppes$new.name3 <- gsub("[[:space:]]$","", df.nppes$new.name2)
df.nppes$new.name4 <- gsub("[[:space:]]*","", df.nppes$new.name3)

aco.part$new.name <- gsub("&", " and ",aco.part$Participant.Legal.Business.Name)
aco.part$new.name <- gsub("\\.", "", aco.part$new.name)
aco.part$new.name <- gsub("[[:punct:]]", " ", aco.part$new.name)
aco.part$new.name <- toupper(aco.part$new.name)
aco.part$new.name2 <- gsub("[[:space:]]+"," ", aco.part$new.name)
aco.part$new.name3 <- gsub("[[:space:]]$","", aco.part$new.name2)
aco.part$new.name4 <- gsub("[[:space:]]*","", aco.part$new.name3)

# from this command I can get 2/3 of aco participants, all of them are organizational participants
nppes.aco <- right_join(df.nppes, aco.part,by = c("new.name4" = "new.name4"))

# check what's left, are they all individuals? No.
tmp <- nppes.aco %>% 
	filter(!is.na(provider_organization_name_legal_business_name)) %>% 
	select(Participant.Legal.Business.Name)
length(unique(tmp$Participant.Legal.Business.Name)) #9716

```
### filter out the un-matched aco participants and match them with individual npi number
#### Remove the suffixes of ACO participant names.
```{r}
tmp <- nppes.aco %>% 
	filter(is.na(provider_organization_name_legal_business_name)) %>% 
	select(new.name3.y , Participant.Legal.Business.Name)
tmp$no_suf <- gsub("\\s(PA)$","", tmp$new.name3.y)
tmp$no_suf <- gsub("\\s(MD)$","", tmp$no_suf)
tmp$no_suf <- gsub("^(DR)\\s","", tmp$no_suf)
tmp$no_suf_no_space <- gsub("[[:space:]]+","",tmp$no_suf)
```
### Match with NPPES names with middle initials
```{r}
df.nppes$mid_init <- gsub("^([[:alpha:]]{1}).*", "\\1", df.nppes$provider_middle_name)
df.nppes$name_mid_init <- paste(df.nppes$provider_first_name, df.nppes$mid_init,
													 df.nppes$provider_last_name_legal_name, sep = " ")
df.nppes$name_mid_init <- gsub("[:punct:]"," ",df.nppes$name_mid_init)
df.nppes$name_mid_init_space <- gsub("[[:space:]]+"," ",df.nppes$name_mid_init)
df.nppes$name_mid_init_no_space <- gsub("[[:space:]]+","",df.nppes$name_mid_init)

nppes.aco.ind.mid.init <- right_join(df.nppes, tmp, by = c("name_mid_init_no_space" = "no_suf_no_space"))

tmp2 <- nppes.aco.ind.mid.init %>% 
	filter(!is.na(provider_organization_name_legal_business_name)) %>% 
	select(Participant.Legal.Business.Name)
length(unique(tmp2$Participant.Legal.Business.Name)) #1501

```
### Match with NPPES names with full middle name
```{r}
tmp2 <- nppes.aco.ind.mid.init %>% 
	filter(is.na(provider_organization_name_legal_business_name)) %>% 
	select(name_mid_init_no_space , Participant.Legal.Business.Name)
names(tmp2) <- c("no_suf_no_space","Participant.Legal.Business.Name")
df.nppes$full_mid <- gsub("[:punct:]", "", df.nppes$provider_middle_name)
df.nppes$name_full_mid <- paste(df.nppes$provider_first_name, df.nppes$full_mid,
													 df.nppes$provider_last_name_legal_name, sep = " ")
df.nppes$name_full_mid <- gsub("[:punct:]"," ",df.nppes$name_full_mid)
df.nppes$name_full_mid_space <- gsub("[[:space:]]+"," ",df.nppes$name_full_mid)
df.nppes$name_full_mid_no_space <- gsub("[[:space:]]+","",df.nppes$name_full_mid)

nppes.aco.ind.full.mid <- right_join(df.nppes, tmp2, by = c("name_full_mid_no_space" = "no_suf_no_space"))

tmp3 <- nppes.aco.ind.full.mid %>%  
	filter(!is.na(provider_organization_name_legal_business_name)) %>% 
	select(Participant.Legal.Business.Name)
length(unique(tmp3$Participant.Legal.Business.Name)) #87
```

```{r}
tmp3 <- nppes.aco.ind.full.mid%>% 
	filter(is.na(provider_organization_name_legal_business_name)) %>% 
	select(name_full_mid_no_space , Participant.Legal.Business.Name)
names(tmp3) <- c("no_suf_no_space","Participant.Legal.Business.Name")
df.nppes$name_no_mid <- paste(df.nppes$provider_first_name,
													 df.nppes$provider_last_name_legal_name, sep = " ")
df.nppes$name_no_mid <- gsub("[:punct:]"," ",df.nppes$name_no_mid)
df.nppes$name_no_mid_space <- gsub("[[:space:]]+"," ",df.nppes$name_no_mid)
df.nppes$name_no_mid_no_space <- gsub("[[:space:]]+","",df.nppes$name_no_mid)

nppes.aco.ind.no.mid <- right_join(df.nppes, tmp3, by = c("name_no_mid_no_space" = "no_suf_no_space"))

tmp4 <- nppes.aco.ind.no.mid %>%  
	filter(!is.na(provider_organization_name_legal_business_name)) %>% 
	select(Participant.Legal.Business.Name)
length(unique(tmp4$Participant.Legal.Business.Name)) #625
```

```{r}
tmp <- nppes.aco %>% 
	filter(!is.na(provider_organization_name_legal_business_name)) %>% 
	select(npi_id,Participant.Legal.Business.Name)
length(unique(tmp$Participant.Legal.Business.Name))
tmp2 <- nppes.aco.ind.mid.init %>% 
	filter(!is.na(provider_organization_name_legal_business_name)) %>% 
	select(npi_id,Participant.Legal.Business.Name)
tmp3 <- nppes.aco.ind.full.mid %>%  
	filter(!is.na(provider_organization_name_legal_business_name)) %>% 
	select(npi_id,Participant.Legal.Business.Name)
tmp4 <- nppes.aco.ind.no.mid %>%  
	filter(!is.na(provider_organization_name_legal_business_name)) %>% 
	select(npi_id,Participant.Legal.Business.Name)

test <- full_join(tmp, tmp2)
test2 <- full_join(test, tmp3)
test3 <- full_join(test2, tmp4)
length(unique(test3$Participant.Legal.Business.Name))


```



########################################
