---
title: "physician-compare-same-group"
author: "Batta Liu"
date: '2016-11-08'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages 
```{r packages, echo=FALSE}
require("RPostgreSQL")
library(plyr)
library(dplyr)
library("ggplot2")
library(ggmap)
library(RDSTK)
library(zipcode)
library(abind)
library(jsonlite)
```
## create a connection
```{r connection, echo=FALSE}
# save the password that we can "hide" it as best as we can by collapsing it
pw <- {
	"no323232"
}

# loads the PostgreSQL driver
drv <- dbDriver("PostgreSQL")

# creates a connection to the postgres database
# note that "con" will be used later in each connection to the database
con <- dbConnect(drv, dbname = "liubatta",
								 host = "192.168.0.10", port = 5432,
								 user = "liubatta", password = pw)

rm(pw) # removes the password

# check for the cartable
dbExistsTable(con, "tmp_test")
```
load the physician compare data
```{r}

df.physician <- dbGetQuery(con, " SELECT * from physician_compare_20160908")
df.npi <- dbGetQuery(con, 
										 " SELECT npi_id,
										 entity_type_code, 
										 healthcare_provider_taxonomy_code_1
										 from npi_20160710")

taxonomy <- read.csv("/Users/batta/Dropbox/phd4/nursing-homes/read/Data/nucc_taxonomy_161.csv")
```
Check how many physicians are in the same practice group.
```{r}
group <- df.physician %>% 
	select(npi,org_pac_id, num_org_mem) %>% 
	unique(.) %>% # remove duplicated obs due to multiple PAC id
	group_by(org_pac_id, num_org_mem) %>% 
	tally %>% 
	arrange(org_pac_id) #179795 practice group

group$partial_medicare <- (group$n-as.numeric(group$num_org_mem)<0) # 1 are TRUE, 1308 doesn't report group practice number
group$misreport <- (group$n-as.numeric(group$num_org_mem)>0) # 288 are TRUE
group$num_org_mem <- as.numeric(group$num_org_mem)
group_all_medicare <- group %>% 
	filter(partial_medicare==FALSE, misreport==FALSE) # 178198 medical groups have full record.
```
Keep only the medical groups with full record. Check the affiliatons of physicians in the same medical group. And compare the results of physicians in the same group.
```{r}
group.physician <- semi_join(df.physician,group_all_medicare, by ="org_pac_id")
affi.physician <- group.physician %>% 
	filter(!is.na(hosp_afl_1))

# check wherther physicians in the same group all have affiliation, answer is no
group.affi <- affi.physician %>% 
	select(npi,org_pac_id, num_org_mem) %>% 
	unique(.) %>% 
	group_by(org_pac_id, num_org_mem) %>% 
	tally %>% 
	arrange(org_pac_id)

# check whether physicians in the same group all have the same affiliation.
group.affi2 <- affi.physician %>% 
	select(org_pac_id, num_org_mem, hosp_afl_1) %>% 
	unique(.) %>% 
	group_by(org_pac_id, num_org_mem,hosp_afl_1) %>% 
	tally %>% 
	arrange

# filter out medical groups with only one hospital affiliation, and check other physicians' link with it. 

tmp <- group.affi2 %>% 
	select(org_pac_id) %>% 
	tally %>% 
	filter(n==1, num_org_mem>1)

group.affi3	<- semi_join(df.physician, tmp, by = "org_pac_id")

```
"group.affi3" contains practices groups affiliated with only one hospital and with more than one physician.
Check physician's taxonomies.
```{r}
df.npi$npi_id <- as.numeric(df.npi$npi_id)
group.affi4 <- left_join(group.affi3, df.npi, by = c("npi"="npi_id")) # add taxonomy information to physician.
tmp <- grep("^(20)",group.affi4$healthcare_provider_taxonomy_code_1) # need to check whether this is correct filter for MD and OD.
group.affi5 <- group.affi4[tmp,]
tmp <- group.affi5 %>% 
	select(npi,org_pac_id, hosp_afl_1) %>% 
	unique(.) %>% 
	group_by(org_pac_id, hosp_afl_1) %>% 
	tally

tmp2 <- tmp %>% 
	select(org_pac_id) %>% 
	tally %>% 
	filter(n>1)

group.affi6 <- semi_join(group.affi5, tmp2, by = "org_pac_id") # groups with only one hospital affiliation, but also has physicians not affiliated with that hospital.

tmp <- group.affi6 %>% 
	select(npi,org_pac_id,hosp_afl_1,healthcare_provider_taxonomy_code_1) %>% 
	unique(.) %>% 
	group_by(org_pac_id,hosp_afl_1,healthcare_provider_taxonomy_code_1) %>% 
	tally

# check whether any misrecord of hospital affiliation, and the answer is no.
tmp2 <- group.affi6 %>% 
	select(npi,hosp_afl_1) %>% 
	unique(.) %>% 
	group_by(npi) %>% 
	tally
unique(tmp2$n)

# check whether any dual-group problem of physician, and the answer is yes.
tmp3 <- group.affi6 %>% 
	select(npi,org_pac_id) %>% 
	unique(.) %>% 
	group_by(npi) %>% 
	tally
unique(tmp3$n)

tmp4 <- tmp3 %>% 
	filter(n==1)

# filter the physicians in only one group.
group.affi7 <- semi_join(group.affi6,tmp4, by = "npi")
```


```{r}

group.affi8 <- semi_join(group.affi7, tmp, by = "npi")

```


